\textbf{Computational Fuzzy Extractors}

### 2013-02-15 CompFuzzExt.tex
Updates to section 3 and associated proofs

\begin{definition}
Let $(X, Y)$ be a pair of random variables.  $X$ has 
\emph{conditional HILL entropy} at least $k$ conditioned on $Y$,
denoted $H^{\hill}_{\epsilon, s_{sec}}(X|Y)\geq k$ if there exists a collection of
distributions $Z_y$ for each $y\in Y$, giving rise to a joint distribution
$(Z, Y)$, such that $\tilde{H}_\infty(Z|Y)\geq k$ and for all (randomized, binary output) circuits $D$ of size $s_{sec}$, $\delta^D((X, Y),(Z,Y))\leq \epsilon$.
\end{definition}

Intuitively, conditional HILL entropy is as good as average min-entropy for all computationally-bounded observers.  Thus, redefining secure sketches using HILL entropy is a  natural relaxation of the original information-theoretic definition; in particular, the construction in \lemref{lem:fuzzy ext construction} would yield pseudorandom outputs if the secure sketch ensured high HILL entropy.  However, as we show in Section~\ref{sec:imp HILL sketch}, such secure sketches can't perform much better than the information-theoretic ones.

Instead, in \secref{sec:unp secure sketch}, we define computational secure sketches using unpredictability, and work with that definition for the rest of the paper.  In particular, in \secref{sec:comp fuzzy extractors}, we show a natural construction of computational fuzzy extractors from secure sketches defined using unpredictability.
%The size of the circuits becomes important, we would like the \rec procedure to be computable by a circuit significantly smaller than the \hill entropy circuit size.  We simply include both of these parameters in the definition.  We review other definitions of computational entropy in Appendix~\ref{sec:notionsEntropy}.

\subsection{Bounds on Secure Sketches using HILL entropy}
\label{sec:imp HILL sketch}
It seems natural to replace a sketch that retains information theoretic entropy with a sketch that retains HILL entropy.  Then the paradigm of secure sketch and average case randomness extractor could be used. However, we show that using this definition it is impossible to beat information theoretic bounds on secure sketches.  We omit formal definitions for the moment and recall the two informal properties we seek:
\begin{itemize}
\item \emph{Correctness}: if $\dis(w, w')\leq t$ then $\rec(w', \sketch(w)) = w$.
\item \emph{Security}: For all $W$ where $H_\infty(W)\geq m$, $H^\hill_{\epsilon, s}(W|\sketch(W))  = \tilde{m}$.
\end{itemize}
%We will concentrate on the case where $gap = m-\tilde{m}=0$ however, any setting where  $gap$ is better than the best information theoretic sketch is still a meaningful result. % As before, we desired $\rec$ to be efficiently computable.  We start with this stronger definition to show the difficulty of constructing such an object.

Unfortunately, we will show if $H^{\hill}_{\epsilon, s}(W|SS(W))= \tilde{m}$ this implies an error correcting code with approximately $2^{\tilde{m}}$ points.  We provide intuition for the argument below and then present the formal argument.  Consider a function $\rec$ where $\rec (w', \sketch(w)) = w$ when $\dis(w, w')\leq t$.  This means in order for $H^{\hill}_{\epsilon, s}(W|SS(W))= \tilde{m}$, there must be a distribution $Y$ where $\Hoo(Y)\geq \tilde{m}$ such that $\Pr_{y\in Y} [y'\leftarrow B_t(y) \wedge \rec(y', \sketch(y)) = y ]\geq 1-\epsilon$.  This means the points in $Y$ form an error correcting code and $\rec$ is an efficient decoder.  We can then use standard arguments to turn this code into an information theoretic sketch.  This means lower bounds on the entropy loss of an information theoretic sketch must apply.  There are several technical conditions required to make this intuition formal, we present them below.
%any function that is able to recover correctly on a large space is an decoder for an error correcting code formed by that space.  If there is a distribution $Y$ with many points such that $\rec(y', \sketch(w)) =y\in Y$ when $\dis(y, y')\leq t$.  Then $\rec$ is a decoder for the error correcting code formed by $Y$.
% and make no assumption about the behavior of $\rec $ outside of this ball.  The intuition is quite simply, on a point $w\leftarrow W$, the \rec oracle will always return $w$ within the $B_t(w)$.  If $W|\sketch(W)$ is indistinguishable from $Y|\sketch(W)$ then the $\rec$ oracle must also correct for points in $Y$.  However, this implies a code~(the points in $Y$) with $\rec$ as an efficient decoding algorithm. 
%\subsubsection{The Uniform Distribution}
%and extend to an arbitrary high-entropy distribution.  
%We begin by showing that any given no distribution $W$ can be indistinguishable from the uniform distribution given a sketch.
%We need two technical requirements on our metric space: 1) there is an efficient algorithm to sample neighbors 2) each point is regular~(has the same number of neighbors).  These requirements hold for several natural metric spaces including Hamming and symmetric difference metrics.
%The only other requirement we make is for the distribution and its neighborhood to be efficiently samplable.
%\begin{definition}
%A distribution $W$ is $s-$\emph{efficiently-samplable} if there exists a randomized circuit of size at most $s$ that outputs samples according to $W$.
%Furthermore, we say $W$ is \emph{efficiently-samplable} if there exists a randomized circuit of polynomial size that outputs samples according to $W$.
%\end{definition}
%We will be working with a metric space $\mathcal{M}, d$.  We will need to efficiently sample nearby points in the metric space.
We assume that sampling a random neighbor of a point is efficient:
\begin{definition}
We say a metric space $(\mathcal{M}, \dis)$ is $(s_{sam}, t)$-\emph{neighborhood efficently-samplable} if there exists a randomized circuit, $\sample$ of size $s_{sam}$ that for all $t'\leq t$, $\sample (x, t')$ outputs a random point at distance $t'$ of $x$.  
%That is $\exists \sample$ of size at most $s$ such that $\forall x\in \mathcal{M},$
%\[
%\Delta(\sample(x, t') , \{x'| \dis(x,x') = t'\})=0
%\]
Furthermore, there is a procedure that outputs a random point of distance at most $t$.  For convenience we denote this procedure by $\sample(X)$.
\end{definition}
We require that \sample returns a point different from $x$ to ensure that each $B_t(x)$ contains at least one other point.  While we could consider metric spaces where balls only contain their center, this is not very interesting in the context of fuzzy extractors~(as \gen can always output the empty string for $P$).

@@

We show that any recovery functionality that retains high HILL entropy implies a information theoretic secure sketch.  We begin by reviewing definitions of Shannon codes~\cite{shannon1949mathematical}:
\begin{definition}
Let $\mathcal{C}$ be a set over space $\mathcal{M}$.  We say that $\mathcal{C}$ is an $(t,\epsilon)$-\emph{Shannon code} if there exists an efficient procedure $\rec$ such that for all $c\in \mathcal{C}$, $\Pr[\rec(\sample(c, t)) \neq c]<\epsilon$.
\end{definition}
This is a slightly nonstandard formulation, we only require the code to correct exactly $t$ errors\footnote{In the standard formulation, the code must correct up to $t$ errors.  For codes that are monotone~(if decoding succeeds on a set of errors, it succeeds on all subsets), these formulations are equivalent.  However, we work with an arbitrary recover functionality that is not necessarily monotone.}.  Shannon codes work for all codewords, we can also consider a formulation that works for an ``average'' codeword.
\begin{definition}
Let $W$ be a distribution over space $\mathcal{M}$.  We say that $W$ is an $(t,\epsilon)$-\emph{average error Shannon code} if there exists an efficient procedure $\rec$ such that 
$\Pr_{w\leftarrow W}[\rec(\sample(w, t)) \neq w]<\epsilon$.
\end{definition}
An average error Shannon code is convertible to a (maximal error)~Shannon code with a small loss.  We use the following pruning argument from Cover and Thomas~\cite[Pages 202-204]{cover2006elements}~(we provide a proof in \secref{sec:proof of average to maximal error}):
\begin{lemma}
\label{lem:averageToMaximalError}
Let $W$ be a distribution with $\Hoo(W)\geq k$ and let $W$ be a $(t, \epsilon)$-average error Shannon code with recovery procedure $\rec$.  There is a set $W'$ where $|W'|\ge2^{k-1}$ and $W'$~(drawing a codeword uniformly) is a $(t, 2\epsilon)$-(maximal error) Shannon code with recovery procedure $\rec$.
\end{lemma}

With this conversion we can show a surprising result: recover functionalities that retain HILL entropy imply Shannon error correcting codes~(proof in \secref{sec:proof of thm sketch implies code}).
\begin{theorem}\label{thm:impSketchArbitraryW}
Let $(\mathcal{M}, \dis)$ be a metric space that is $(s_{neigh}, t)$-neighborhood samplable.  Let $(\sketch, \rec)$ be an $(s_{rec}, t)$-recover functionality over $\mathcal{M}$.  If $H^{\hill}_{\epsilon, s_{sec}}(X|SS(X))\geq k$ then there exists $x$ and a set $W'$ where $|W'|\geq 2^{k-1}$ such that for all $1\leq t'\leq t$, $W'$ is a $(t', 2\epsilon)$-Shannon code with recovery procedure $\rec(\cdot, \sketch(x))$ for $s_{sec}= \Omega(t(s_{neigh}+s_{rec}))$.
%Let $W$ be a flat distribution~(all points in the support of $W$ have the same probability) over $\mathcal{M}$ where $\Hoo(W)\geq k$ and   Let $X$ be arbitrarily but independently distributed over $\mathcal{M}$.  If $\delta^D((X, \sketch(X)), (W, \sketch(X)))<\epsilon$ for negligible $\epsilon$ and $D$ of size at least $O(s_{neigh}+s_{rec})$, then $\exists x, W'$ where $|W'|\geq |W|/2 \geq 2^{k-1}$ such that $W'$ is a $(t, 2\epsilon)$ Shannon code with recovery procedure $\rec(\cdot, \sketch(x))$.
\end{theorem}
%The code provided in \thref{thm:impSketchArbitraryW} is weaker than a Shannon error correcting code~\cite{shannon1948}.  In a Shannon code, for all codewords $c, \Pr[c'\leftarrow \sample(c) \wedge \rec(c') \neq c]<\epsilon$.  Bounds for this type of code are well known~\cite{shannon1948} and efficient constructions exist~\cite{forney1966}.  Requiring proper decoding for only a random codeword is a significant restriction particularly in the case where the probability of outcomes in $W$ differs significantly~(e.g. where $\exists w_1,w_2\in W$ such that $\Pr[W=w_1]/\Pr[W=w_2] = \ngl$).  However, this is still a meaningful set of error correcting codes.  A similar question is considered in Appendix C of \cite{DBLP:journals/siamcomp/DodisORS08}.  They are able to achieve results for Hamming codes~(as they are not restricted to sampling a polynomial portion of the space)\bnote{expand on this explanation}.

We can use techniques from information reconciliation~\cite{smith2007scrambling} and privacy amplification~\cite{bennett1988privacy} to convert any  Shannon code into an information theoretic security sketch~(see \cite[Section 8.2]{DBLP:journals/siamcomp/DodisORS08}):
\begin{lemma}
\label{lem:shannon to sketch}
Let $t$ be a parameter.  Let $\mathcal{C}$ over $\{0,1\}^n$ be a set such that for all $1\leq t'\leq t$, $\mathcal{C}$ is a $(t', \epsilon)$ Shannon code with recovery procedure $\rec'$.  Let $W$ be a distribution with $\Hoo(W)\geq k$.  Define the following procedures
\begin{center}
\begin{tabular}{c|c}
\begin{minipage}{3in}
\textbf{\sketch}
\begin{enumerate}
\item Input $w\leftarrow W$.
\item Sample $\pi$ from the space of all permutations from $\pi: [n]\rightarrow [n]$.
\item Sample $c\leftarrow \mathcal{C}$.
\item Apply $\pi$ bitwise to get $x_i = w_{\pi(i)}$.
\item Output $p = x \oplus c, \pi$.
\end{enumerate}
 \end{minipage} &
\begin{minipage}{3in}
\textbf{\rec}
\begin{enumerate}
\item Input $(w', p, \pi)$
\item Apply $\pi^{-1}$ bitwise to get $x_i' = w_{\pi(i)}$.
\item Compute $c' = p \oplus x'$.
\item Compute $c = \rec'(c)$.
\item Output $p\oplus c$.
\\
\end{enumerate}
\end{minipage} 
\end{tabular}
\end{center}
Then $(\sketch, \rec)$ is a $(\{0,1\}^n, k, k-(n-\log |\mathcal{C}|), t, \epsilon)$ approximately correct secure sketch. 
%satisfies the following properties~(probability over the choice of $\pi$ in $\sketch$):
%\begin{itemize}
%\item Correctness: $\forall w, w'$ where $dis(w, w')\leq t$, $\Pr[\rec(w', \sketch(w))\neq w]<\epsilon$.
%\item Security: $\Hav(W |\sketch(W)) \geq \Hoo(W) - (n-\log |C|)$.
%\item Efficiency: $\sketch$ is efficient if sampling from $C$ is efficient and $\rec$ is efficient if $\rec'$ is efficient.
%\end{itemize}
\end{lemma}
%\begin{construction}
%Let $\delta >0$ be a parameter.
%Let $C$ be a $(t, \epsilon)$ Shannon code over $\{0,1\}^n$.  Choose a permutation $\pi:\mathcal{M}rightarrow \mathcal{M}$ that is $\beta$-almost independent $\ell = \delta n/\log(n)$-wise permutation.  Thefn for $\beta = 2^{-\ell}
%\end{construction}
Putting together \thref{thm:impSketchArbitraryW} and \lemref{lem:shannon to sketch} gives our main negative result.  Any recover functionality that retains HILL entropy implies an information theoretic sketch:
\begin{corollary}
\label{cor:rec yields sketch}
Let $(\sketch', \rec')$ be a $(s_{rec}, t)$-recover functionality over $\{0,1\}^n$ such that $H^{\hill}_{\epsilon, s_{sec}}(X | \sketch'(X))\geq k$.  If $s_{sec}=\Omega(t(s_{rec} + n))$,  then for all $W$ with $\Hoo(W)\geq m$ there exists a $(\{0,1\}^n, m, m-(n-k+1), 2\epsilon)$ (information-theoretic) approximately correct secure sketch.
%Let $(\mathcal{M}, d)$ be a metric space that is $(s_{neigh}, t)$-neighborhood samplable.  If no $(t, \epsilon)$-average error Shannon code over $\mathcal{M}$ exists of size $2^k$ then, $\forall (s_{rec}, t)$ recovery procedures $(\sketch, \rec)$ $H^{\hill}_{\epsilon, s}(X|\sketch(X))\not\geq k$ for $s=O(s_{rec}+s_{neigh})$.
\end{corollary}
\textbf{Note:} In \corref{cor:rec yields sketch} we make no claim about the feasibility of constructing $(\sketch, \rec)$.  Several steps in \thref{thm:impSketchArbitraryW} are not constructive so there may not be an efficient procedure for $\sketch$.

\corref{cor:rec yields sketch} shows that sketches that retain HILL entropy can be converted into an information-theoretic sketch.  Unfortunately, we have lower bounds for the entropy drop for information-theoretic sketches:

\begin{proposition}\protect{\cite[Proposition 8.2]{DBLP:journals/siamcomp/DodisORS08}}
\label{prop:lower bound entropy drop}
For any error rate $1\leq t\leq n$, any secure sketch which corrects $t$ random errors with probability at least $2/3$ has entropy loss at least $n(h(t/n) -o(1))$; that is, $\Hav(W|\sketch(W))\leq n (1-h(t/n) - o(1))$ when $W$ is drawn uniformly from $\{0,1\}^n$.  Here $h(\cdot)$ is the binary entropy function.
\end{proposition}

Together \corref{cor:rec yields sketch} and \propref{prop:lower bound entropy drop} say the entropy drop for a ``HILL sketch'' must be the same as the entropy drop of a sketch that corrects random errors.  This entropy drop is tied to the Shannon capacity.  Furthermore, we have information theoretic constructions that meet these bounds.  Thus, defining a computational secure sketch using HILL entropy is unlikely to be useful.

@@

\begin{construction}
Let $n$ be a security parameter and let $m>n$.  %Let $W = W_1,..., W_m$ and let $b$ be a constant and let $W_i \in \zo^b$ for all $i$.  
Define $\sketch, \rec$ as follows:%The following construction is a computational secure sketch:
%Code-offset construction of a secure sketch using a random linear code over a finite field $\Fq$. $\mathcal{I}_t (\vA, \vect{D})$ denotes an algorithm that decodes up to $t$ errors, i.e., an algorithm that finds $X'\in \Fq^n$ such that $\vect{A}X'$ is of Hamming distance at most $t$ from $\vect{D}$. $m > n$ are parameters to be figured out later.
\begin{center}
\begin{tabular}{c|c}
\begin{minipage}{3in}
\textbf{\sketch}
\begin{enumerate}
\item \underline{Input}: $w\leftarrow W$ (where $W$ is some distribution over $\Fq^m$).
\item Sample $\vA\in\Fq^{m\times n}, X\in\Fq^n$ uniformly.
\item Output $s = (\vA, \vA X+w)$.
\\
\end{enumerate}
 \end{minipage} &
\begin{minipage}{3in}
\textbf{\rec}
\begin{enumerate}
\item \underline{Input}: $(w', s)$ (where the Hamming distance between $w'$ and $w$ is at most $t$).
\item Parse $s$ as $(\vA, \vect{C})$; let $\vect{D}=\vect{C}-w'$.
\item Let $X' = \mathcal{I}_t(\vA, \vect{D})$\\
Set $X'_{1,..., n}$ be the first half bits of $X'$.		 
\item Output $X'_{1,...,n}$.
\end{enumerate}
\end{minipage} 
\end{tabular}
\end{center}
\label{cons:informal construction}
\end{construction}

>>>>

\begin{definition}
Let $(X, Z)$ be a pair of random variables.  $X$ has 
\emph{conditional HILL entropy} at least $k$ conditioned on $Z$,
denoted $H^{\hill}_{\epsilon, s_{sec}}(X|Z)\geq k$ if there exists a collection of
distributions $Y_z$ for each $z\in Z$, giving rise to a joint distribution
$(Y, Z)$, such that $\tilde{H}_\infty(Y|Z)\geq k$ and $\delta^{\mathcal{D}_{s_{sec}}} ((X, Z),(Y,Z))\leq \epsilon$.
\end{definition}

Intuitively, conditional HILL entropy is as good as average min-entropy for all computationally-bounded observers.  Thus, redefining secure sketches using HILL entropy is a  natural relaxation of the original information-theoretic definition; in particular, the construction in \lemref{lem:fuzzy ext construction} would yield pseudorandom outputs if the secure sketch ensured high HILL entropy.  However, as we show in Section~\ref{sec:imp HILL sketch}, such secure sketches cannot  perform much better than the information-theoretic ones.

Instead, in \secref{sec:unp secure sketch}, we relax the definition by allowing by outputting a new random variable that can be recovered when $\dis (w, w')\leq t$.  This object is the computational analogue of a noisy conductor~\cite{KanukurthiR09}.%This is a noisy computational conductor define computational secure sketches using unpredictability, and work with that definition for the rest of the paper.  
  In \secref{sec:comp fuzzy extractors}, we show that computational fuzzy extractors can be constructed from noisy computational conductors.
%The size of the circuits becomes important, we would like the \rec procedure to be computable by a circuit significantly smaller than the \hill entropy circuit size.  We simply include both of these parameters in the definition.  We review other definitions of computational entropy in Appendix~\ref{sec:notionsEntropy}.

\subsection{Bounds on Secure Sketches using HILL entropy}
\label{sec:imp HILL sketch}
Suppose we redefine secure sketches using HILL entropy: that is, an \emph{$(\epsilon,s_{sec})$-HILL-entropy secure sketch} is the same object as in Definition~\ref{def:secure sketch}, but the security requirement is replaced with  $H^{\hill}_{\epsilon, s_{sec}}(W|\sketch(W))\geq \tilde{m}$. 
Unfortunately, we will show below that such a secure sketch implies an error correcting code with approximately $2^{\tilde{m}}$ points that can correct $t$ random errors (see  \cite[Lemma C.1]{DBLP:journals/siamcomp/DodisORS08} for a similar bound on information-theoretic secure sketches). For the Hamming metric, our result essentially matches the bound on information-theoretic secure sketches of \cite[Proposition 8.2]{DBLP:journals/siamcomp/DodisORS08}.  In fact, we show that, for the Hamming metric, HILL-entropy secure sketches imply information-theoretic ones with similar parameters, and, therefore, the HILL relaxation gives no advantage.

The intuition for building error-correcting codes from HILL-entropy secure sketches is as follows. Consider a function $\rec$ where $\rec (w', \sketch(w)) = w$ when $\dis(w, w')\leq t$.  When we consider the distribution $W$, to have  $H^{\hill}_{\epsilon, s_{sec}}(W|\sketch(W))\ge \tilde{m}$, there must be a distribution $Y$ with $\Hav(Y | \sketch(W))\geq \tilde{m}$ and $Y| \sketch(W)$ is computationally indistinguishable from $W | \sketch(W)$.  Since we know that $\rec$ succeeds with high probability, this means $\rec$ must succeed on $Y$ with high probability.  In particular, $\Pr_{y\in Y} [y'\leftarrow B_t(y) \wedge \rec(y', \sketch(y)) = y ]\geq 1-\epsilon$.  This means we can construct a set $C$ out of the points in the support of $Y$.  Then $C$ will be an error correcting code and $\rec$ an efficient decoder.  We can then use standard arguments to turn this code into an information theoretic sketch.  
%\lnote{this intuition is confusing, esp. given notational inconsistencies of all the capital letters with what comes above and below}
To make this intuition precise, we need an additional technical condition:  sampling a random neighbor of a point is efficient.
\begin{definition}
We say a metric space $(\mathcal{M}, \dis)$ is $(s_{sam}, t)$-\emph{neighborhood efficently-samplable} if there exists a randomized circuit $\sample$ of size $s_{sam}$ that for all $t'\leq t$, $\sample (x, t')$ outputs a random point at distance $t'$ of $x$.  
%That is $\exists \sample$ of size at most $s$ such that $\forall x\in \mathcal{M},$
%\[
%\Delta(\sample(x, t') , \{x'| \dis(x,x') = t'\})=0
%\]
\end{definition}
We require that \sample returns a point different from $x$ to ensure that each $B_t(x)$ contains at least one other point.  While we could consider metric spaces where balls only contain their center, secure sketches are not interesting in this context.

@@

We review definitions of Shannon codes~\cite{shannon1949mathematical}:
\begin{definition}
Let $\mathcal{C}$ be a set over space $\mathcal{M}$.  We say that $\mathcal{C}$ is an $(t,\epsilon)$-\emph{Shannon code} if there exists an efficient procedure $\rec$ such that for all $t'\le t$ and for all $c\in \mathcal{C}$, $\Pr[\rec(\sample(c, t')) \neq c]<\epsilon$. To distinguish it from the average-error Shannon code defined below, we will sometimes call it \emph{maximal-error} Shannon code.
\end{definition}
This is a slightly stronger formulation than usual, in that we require the code to correct random errors of every size $t'<t$. \footnote{In the standard formulation, the code must correct a random error of size up to $t$, which may not imply that it can correct a random error of a much smaller size $t'$, because the volume of the ball of size $t'$ may be negligible compare to the volume of the ball of size $t$.  For codes that are monotone~(if decoding succeeds on a set of errors, it succeeds on all subsets), these formulations are equivalent.  However, we work with an arbitrary recover functionality that is not necessarily monotone.}.

Shannon codes work for all codewords. We can also consider a formulation that works for an ``average'' codeword. \begin{definition}
Let $C$ be a distribution over space $\mathcal{M}$.  We say that $C$ is an $(t,\epsilon)$-\emph{average error Shannon code} if there exists an efficient procedure $\rec$ such that for all $t'\le t$
$\Pr_{c\leftarrow C}[\rec(\sample(c, t')) \neq c]<\epsilon$.
\end{definition}
An average error Shannon code is convertible to a maximal error Shannon code with a small loss.  We use the following pruning argument from Cover and Thomas~\cite[Pages 202-204]{cover2006elements} (we provide a proof in \secref{sec:proof of average to maximal error}):
\begin{lemma}
\label{lem:averageToMaximalError}
Let $C$ be a distribution with $\Hoo(C)\geq k$ and let $C$ be a $(t, \epsilon)$-average error Shannon code with recovery procedure $\rec$.  There is a set $C'$ with $|C'|\ge2^{k-1}$ that  is a $(t, 2\epsilon)$-(maximal error) Shannon code with recovery procedure $\rec$.
\end{lemma}

We are now ready to show our main result: HILL-entropy secure sketches imply maximal-error Shannon codes~(proof in \secref{sec:proof of thm sketch implies code}).
\begin{theorem}\label{thm:impSketchArbitraryW}
Let $(\mathcal{M}, \dis)$ be a metric space that is $(s_{neigh}, t)$-neighborhood samplable.  Let $(\sketch, \rec)$ be an $(\epsilon,s_{sec})$-HILL-entropy $(\mathcal{M}, m, \tilde{m}, t)$-secure sketch with error $\delta$.  Assume $s_{sec}= \Omega(t(s_{neigh}+s_{rec}))$, where $s_{rec}$ is the circuit size of $\rec$.  Then there exists $x$ and a set $C$ with $|C'|\geq 2^{\tilde{m}-1}$ that is a $(t, 2(\epsilon+\delta))$-Shannon code with recovery procedure $\rec(\cdot, \sketch(x))$.
%Let $W$ be a flat distribution~(all points in the support of $W$ have the same probability) over $\mathcal{M}$ where $\Hoo(W)\geq k$ and   Let $X$ be arbitrarily but independently distributed over $\mathcal{M}$.  If $\delta^D((X, \sketch(X)), (W, \sketch(X)))<\epsilon$ for negligible $\epsilon$ and $D$ of size at least $O(s_{neigh}+s_{rec})$, then $\exists x, W'$ where $|W'|\geq |W|/2 \geq 2^{k-1}$ such that $W'$ is a $(t, 2\epsilon)$ Shannon code with recovery procedure $\rec(\cdot, \sketch(x))$.
\end{theorem}
%The code provided in \thref{thm:impSketchArbitraryW} is weaker than a Shannon error correcting code~\cite{shannon1948}.  In a Shannon code, for all codewords $c, \Pr[c'\leftarrow \sample(c) \wedge \rec(c') \neq c]<\epsilon$.  Bounds for this type of code are well known~\cite{shannon1948} and efficient constructions exist~\cite{forney1966}.  Requiring proper decoding for only a random codeword is a significant restriction particularly in the case where the probability of outcomes in $W$ differs significantly~(e.g. where $\exists w_1,w_2\in W$ such that $\Pr[W=w_1]/\Pr[W=w_2] = \ngl$).  However, this is still a meaningful set of error correcting codes.  A similar question is considered in Appendix C of \cite{DBLP:journals/siamcomp/DodisORS08}.  They are able to achieve results for Hamming codes~(as they are not restricted to sampling a polynomial portion of the space)\bnote{expand on this explanation}.

It is known (see \cite[Section 8.2]{DBLP:journals/siamcomp/DodisORS08} and references therein) that, for the Hamming metric, any Shannon code (in the stronger sense defined by us) can be converted into an information-theoretic secure sketch.  The idea is to use the code offset construction, but randomize the order of the bits of $w$ first, via  permutation $\pi$  (which  becomes part of the sketch and is applied to $w'$ during $\rec$). The formal statement is in the following Lemma.
\begin{lemma}
\label{lem:shannon to sketch}
For an alphabet $Z$, let $\mathcal{C}$ over $Z^n$ be a $(t, \delta)$ Shannon code.% with recovery procedure $\rec'$.
%  Let $W$ be a distribution with $\Hoo(W)\geq k$. 
%
% Define the following procedures
%\lnote{I think this description is buggy}
%\begin{center}
%\begin{tabular}{c|c}
%\begin{minipage}{3in}
%\textbf{\sketch}
%\begin{enumerate}
%\item Input $w\leftarrow W$.
%\item Sample $\pi$ from the space of all permutations from $\pi: [n]\rightarrow [n]$.
%\item Sample $c\leftarrow \mathcal{C}$.
%\item Apply $\pi$ bitwise to get $x_i = w_{\pi(i)}$.
%\item Output $p = x \oplus c, \pi$.
%\end{enumerate}
% \end{minipage} &
%\begin{minipage}{3in}
%\textbf{\rec}
%\begin{enumerate}
%\item Input $(w', p, \pi)$
%\item Apply $\pi^{-1}$ bitwise to get $x_i' = w_{\pi(i)}$.
%\item Compute $c' = p \oplus x'$.
%\item Compute $c = \rec'(c)$.
%\item Output $p\oplus c$.
%\\
%\end{enumerate}
%\end{minipage} 
%\end{tabular}
%\end{center}
Then there exists a $(Z^n, m, m-(n\log|Z|-\log |\mathcal{C}|), t)$ secure sketch with error $\delta$ for the Hamming metric over $Z^n$. 
%satisfies the following properties~(probability over the choice of $\pi$ in $\sketch$):
%\begin{itemize}
%\item Correctness: $\forall w, w'$ where $dis(w, w')\leq t$, $\Pr[\rec(w', \sketch(w))\neq w]<\epsilon$.
%\item Security: $\Hav(W |\sketch(W)) \geq \Hoo(W) - (n-\log |C|)$.
%\item Efficiency: $\sketch$ is efficient if sampling from $C$ is efficient and $\rec$ is efficient if $\rec'$ is efficient.
%\end{itemize}
\end{lemma}
%\begin{construction}
%Let $\delta >0$ be a parameter.
%Let $C$ be a $(t, \epsilon)$ Shannon code over $\{0,1\}^n$.  Choose a permutation $\pi:\mathcal{M}rightarrow \mathcal{M}$ that is $\beta$-almost independent $\ell = \delta n/\log(n)$-wise permutation.  Thefn for $\beta = 2^{-\ell}
%\end{construction}
Putting together \thref{thm:impSketchArbitraryW} and \lemref{lem:shannon to sketch} gives us the negative result for the Hamming metric: a HILL-entropy secure sketch (for the uniform distribution) implies an information-theoretic one with similar parameters:
\begin{corollary}
\label{cor:rec yields sketch}
Let $Z$ be an alphabet. Let $(\sketch', \rec')$ be an $(\epsilon,s_{sec})$-HILL-entropy $(Z^n, n\log |Z|, \tilde{m}, t)$-secure sketch with error $\delta$ for the Hamming metric over $Z^n$, with $\rec'$ of circuit size $s_{rec}$.
If $s_{sec}=\Omega(t(s_{rec} + n))$, then there exists a   $(Z^n, n\log |Z|, \tilde{m}-1,t)$ (information-theoretic) secure sketch with error
$2(\epsilon+\delta)$. 
%Let $(\mathcal{M}, d)$ be a metric space that is $(s_{neigh}, t)$-neighborhood samplable.  If no $(t, \epsilon)$-average error Shannon code over $\mathcal{M}$ exists of size $2^k$ then, $\forall (s_{rec}, t)$ recovery procedures $(\sketch, \rec)$ $H^{\hill}_{\epsilon, s}(X|\sketch(X))\not\geq k$ for $s=O(s_{rec}+s_{neigh})$.
\end{corollary}
\textbf{Note:} In \corref{cor:rec yields sketch} we make no claim about the efficiency of the resulting  $(\sketch, \rec)$, because the proof of \thref{thm:impSketchArbitraryW} is not constructive.

%\corref{cor:rec yields sketch} shows that sketches that retain HILL entropy can be converted into an information-theoretic sketch.  Unfortunately, we have lower bounds for the entropy drop for information-theoretic sketches:

%\begin{proposition}\protect{\cite[Proposition 8.2]{DBLP:journals/siamcomp/DodisORS08}}
%\label{prop:lower bound entropy drop}
%For any error rate $1\leq t\leq n$, any secure sketch which corrects $t$ random errors with probability at least $2/3$ has entropy loss at least $n(h(t/n) -o(1))$; that is, $\Hav(W|\sketch(W))\leq n (1-h(t/n) - o(1))$ when $W$ is drawn uniformly from $\{0,1\}^n$.  Here $h(\cdot)$ is the binary entropy function.
%\end{proposition}

%Together \corref{cor:rec yields sketch} and \propref{prop:lower bound entropy drop} say the entropy drop for a ``HILL sketch'' must be the same as the entropy drop of a sketch that corrects random errors.  This entropy drop is tied to the Shannon capacity.  Furthermore, we have information theoretic constructions that meet these bounds.  Thus, defining a computational secure sketch using HILL entropy is unlikely to be useful.

@@

\begin{construction}
Let $n$ be a security parameter and let $m>n$.  %Let $W = W_1,..., W_m$ and let $b$ be a constant and let $W_i \in \zo^b$ for all $i$.  
Define $\sketch, \rec$ as follows:%The following construction is a computational secure sketch:
%Code-offset construction of a secure sketch using a random linear code over a finite field $\Fq$. $\mathcal{I}_t (\vA, \vect{D})$ denotes an algorithm that decodes up to $t$ errors, i.e., an algorithm that finds $X'\in \Fq^n$ such that $\vect{A}X'$ is of Hamming distance at most $t$ from $\vect{D}$. $m > n$ are parameters to be figured out later.
\begin{center}
\begin{tabular}{c|c}
\begin{minipage}{3in}
\textbf{\sketch}
\begin{enumerate}
\item \underline{Input}: $w\leftarrow W$ (where $W$ is some distribution over $\Fq^m$).
\item Sample $\vA\in\Fq^{m\times n}, X\in\Fq^n$ uniformly.
\item Output $s = (\vA, \vA X+w)$.
\\
\\
\end{enumerate}
 \end{minipage} &
\begin{minipage}{3in}
\textbf{\rec}
\begin{enumerate}
\item \underline{Input}: $(w', s)$ (where the Hamming distance between $w'$ and $w$ is at most $t$).
\item Parse $s$ as $(\vA, \vect{C})$; let $\vect{D}=\vect{C}-w'$.
\item Let $X = \mathcal{I}_t(\vA, \vect{D})$\\
Set $X_{1,..., n/2}$ be the first of $X$.		 
\item Output $X_{1,...,n/2}$.
\end{enumerate}
\end{minipage} 
\end{tabular}
\end{center}
\label{cons:informal construction}
\end{construction}
